Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-01-18 draft.tex
expand related work section

>>>>

	Several researchers have already followed similar or relevant directions to that of this work.
	This section will summarize some efforts in previous research categorized by the use of
	perceptible features or attempts to create explainable models.
	\subsection{Perceptible Features}
	The work of Barrington et al. \cite{barrington_single_2023} explores the idea of classification
	using perceptible features, highlighting their potential for improving explainability in the
	space of deepfake audio detection. They do, however also demonstrate a drop in performance in
	comparison with imperceptible hand-crafted and deep-learning features.
	\newline
	Chaiwongyen et al. \cite{chaiwongyen_contribution_2022,chaiwongyen_deepfake-speech_2023} also
	approach using perceptible features for classification in their works, resulting in lackluster
	performance in 2022, with better results using an expanded and improved feature set in 2023.
	\newline
	Li et al. \cite{li_comparative_2022} also approach perceptible features in their work,
	combining them with imperceptible (referred to as physical in the work) features and using
	various neural networks in their experiments. Overall, the combination of perceptible and
	imperceptible features was able to produce the best performance results of the experiments
	tried.
	\subsection{Explainable Models}
